Proposed Solution

### 2016-11-14 Ennan-Proposal/agenda.tex
stuff

\section{Research Agenda}

The primary work involved in this project
falls into three broad categories:
(i) defining a more comprehensive language model,
(ii) developing new learning algorithms, and
(iii) developing and evaluating \app
  in real-world configuration files.

\subsection{Defining A More Comprehensive Language Model}

While we feel our proposed language model to be relatively comprehensive
to capture many tricky misconfiguration cases,
we will need to define a better language model to represent more types of
configuration files. The configuration files of some of software systems, 
\eg, squid, are not limited to the key-value parameters; thus,
we need to extend the current language model in order to represent
the configuration files of these systems.
In addition, some other types of latent configuration errors 
have been exposed by recent work~\cite{xu16early}.
For example, the path parameter in a MySQL configuration file
has an unknown user account. Such an error cannot be represented in
our proposed language model. Thus, we need to improve it to capture
more error types.

\subsection{Proposing New Learning Algorithms}

We are planning to develop new learning algorithm capable of extracting
rules more accurately and efficiently. We plan to first investigate 
some existing learning algorithms for learning program rules, \eg,
Raychev {\em et al.}~\cite{raychev15predicting, raychev16learning},
and then adapt these algorithms to our scenario, \ie, learning 
the configuration file rules.

\subsection{Deploying and Evaluating \app In Real-World Services}

The project's third main task is to prototype \app and make \app
practical to real-world misconfiguration verification,
thus making \app become a useful tool in practice.
We plan to evaluate the \app prototype's efficiency, usability, and
accuracy using a variety of micro- and macrobenchmarks.
For example, we can evaluate the efficiency and accuracy of 
each module of \app, thus understanding \app's practicality.
More importantly, we will use \app to detect real-world configuration
files~\cite{configdataset}, and then manually check whether \app is able
to successfully detect potential configuration files.

>>>>

\section{Project Timeline}

The proposed project is supposed to last three years. We have identified three main 
goals of the project, each of them taking approximately a year:
\begin{description}
\item[Language Model] 
Our language model has to be expressive enough to be able to express and detect 
many non-trivial misconfiguration cases.
We will, therefore, need to define a more comprehensive language model (than the one presented).  The configuration files of some of software systems, 
\eg, squid, are not limited to the keyword-value parameters; thus,
we need to extend the current language model.
\item [Learning Algorithms]
We outlined basic learning algorithms. However, those are just outlines and
many details are left unspecified.
As we pointed out, especially in the 
probabilistic learner case finding the right thresholds will be one of the main tasks.
We plan to investigate some existing learning algorithms for programs, \eg,
Raychev {\em et al.}~\cite{raychev15predicting, raychev16learning}. 
However, the configuration files have a specific structure and directly applying 
existing rules will not be possible. We will try to adapt some of these algorithms 
to our problem.
\item [Real-Wolrd Evaluation]
Finally, we will implement and evaluate \app on real world misconfigurations.
In addition to evaluating \app on TravisCI files, during the development process 
we will empirically  evaluate efficiency, usability, and
accuracy of \app. We plan to use the existing publicly available dataset of 
misconfigurations~\cite{configdataset}. The set is large enough to use some parts as a  training data and some parts for evaluation.
\end{description}

### 2016-11-14 Ennan-Proposal/impact.tex
stuff

\item {\bf Complementing post-failure error diagnosis efforts.}
  There have been many diagnosis and troubleshooting efforts to localize
  the root causes of configuration errors after system failures occur.
  We call these approaches as post-failure error diagnosis efforts.
  \app will offer a pre-failure error checking
  which could be looked as a preliminary checking before installing
  systems. Because \app is able to find out many sophisticated 
  configuration errors, it removes many labors of 
  the post-failure error diagnosis tools. In addition, the results
  output by \app could be used as a guidance for all the post-failure
  error diagnosis approaches, making these approaches more efficient.

>>>>

\item {\bf Complementing post-failure error diagnosis efforts.}
  There is a number of diagnosis and troubleshooting efforts to localize
  the root causes of configuration errors after system failures occur.
  \app's approach of pre-failure error checking
  can be seen as a preliminary checking before installing a
  system. Because \app cab detect many non-trivial
  configuration errors, it simplifies work for
  post-failure error diagnosis tools. Additionally, the output results
  of \app can be used as a guidance for post-failure
  error diagnosis approaches, making them more efficient.

### 2016-11-14 Ennan-Proposal/intro.tex
stuff

\section*{\app: Automated Verification of Configuration Files}
\paragraph{Overview:} 
Configuration errors (also known as misconfigurations) have become one of the major causes of system failures, resulting in security vulnerabilities, application outages, and incorrect program executions. 
Configuration errors were reported to be the largest fraction of failures in storage systems in a 2014 industry survey. 
Although many techniques have been proposed for configuration error detection, these approaches mainly can only be applied after an error has occurred.
Tools which detect misconfigurations at compile time often require the user to explicitly define constraints, a time consuming and error prone task.
We propose a framework to statically verify configuration files based on automatically generated constraints that define a correct file.
The core idea is to analyze many examples of configuration files from widely available datasets and derive a language model (a set of constraints) that can be used to verify new configuration files.

There are many datasets of configuration files online, but we only know that most are correct - some may be incorrect.
These files will be unlabelled so we do not know if a particular file is correct or incorrect.
Furthermore, both the syntax and semantics of configuration files are notoriously underspecified
Since we are building a general tool to work with any configuration language, \app must be able to handle probabilistic learning in many dimensions.

>>>>

\section*{\app: Automated Verification of Configuration Files}
\paragraph{Overview:} 
Configuration errors (also known as misconfigurations) have become one of the major causes of system failures, resulting in security vulnerabilities, application outages, and incorrect program executions. 
Configuration errors were reported to be the largest fraction of failures in storage systems in a 2014 industry survey. 
Although many techniques have been proposed for configuration error detection, these approaches mainly can only be applied after an error has occurred.
We cannot simply apply techniques that exist for software verification: configuration files mainly consists of sequences of assigning some values to system variables.
Additionally, there is no formal specification describing properties of configuration files.

We propose a framework for automated verification of configuration files. We first automatically derive a specification, and the we check if a given configuration 
file adheres to that specification.
The main idea is to analyze a large number of configuration files from publicly available datasets and derive a corresponding specification. To do that we first develop a language model for configuration files. One question we 
need to address is what if there is an error in the given training set. Our proposed framework 
is general enough that it can still derive a correct specification, under 
the assumption that the same error does not appear in a significant amount of files.
